Synthesizing Quotient Lenses

### 2018-02-09 papers/QuotientLenses/main.tex
added asts count graph

\newcommand{\QRESize}{QS}
\newcommand{\CanonizerAndSpecSize}{CS}
\newcommand{\LensAndSpecSize}{LS}

@@

@@

Figure~\ref{?} shows the number of benchmarks written with at most a given
number of AST nodes.  We found that \QRESize{} was consistently smaller than
\CanonizerAndSpecSize{} and \LensAndSpecSize{}, demonstrating that introducing
QREs saves programmers programming effort compared to both Optician and basic
Boomerang.

>>>>

\newcommand{\QRESize}{\textbf{QS}}
\newcommand{\CanonizerAndSpecSize}{\textbf{CS}}
\newcommand{\LensAndSpecSize}{\textbf{LS}}

@@

\begin{figure}
\includegraphics{generated-graphs/asts.eps}
\caption{Count of benchmark programs definable using a given AST count. We find
  that it takes far fewer AST nodes to define benchmark lenses in \Name{} than
  with Optician or without synthesis. }
\label{fig:asts}
\end{figure}

@@

Figure~\ref{fig:asts} shows the number of benchmarks written with at most a
given number of AST nodes. For a given benchmark, we found \QRESize{} to be
about half as large as \CanonizerAndSpecSize, and about a third as large as
\LensAndSpecSize{}. This demonstrates that introducing QREs saves programmers
significant effort compared to both Optician and basic Boomerang.
